Fluid structure interaction with ETVF

### 2021-03-27 manuscript/paper.tex
Write elastic dam break theory.

This is to test fluid structure interaction.

>>>>

A block of fluid, which is suddenly released under gravity hits an elastic
plate. This benchmark is simulated in many papers.

The material properties of the elastic gate are as follows, and Young's
modulus of $0.01 GPa$ with a Poisson ratio of $0.35$ and a density of
$2500 kg/m^3$.

The length of the fluid block is taken as $0.1m$, and the height is $0.3m$,
and the length of the elastic gate is $0.03m$ with a height of $0.05m$ and is
placed at a distance of $0.1m$ from the end of the fluid block.

As the simulation starts the fluid starts flowing under the influence of
gravity and after some time, it hits the elastic gate. Due to the influence of
the fluid the elastic gate deforms and due to the elastic gate the fluid
starts raising. The dynamics of both mediums is influenced by one another.

We have compared the the tip of the elastic gate with time against the
experimental results produced by \cite{xxx}. As can be seen the results
produced by the current scheme are accurate and are able to reproduce the
experimental results.
